Physcraper: A Python package for continually updated phylogenetic trees using the Open Tree of Life

### 2021-04-06 sources/bmc_template_submission/bmc_article.tex
fixing uppercases

Most of the default thresholds parameter values and software choices in the Physcraper pipeline are arbitrary.
We hope that by making the process of locating homologous sequences online reproducible,
and tracking what cutoffs are used, we make it easier for researchers to delve into the effect that different choices have on their inferences.
In addition, by providing the output files at each step of the analysis,
it is straightforward to assess how changing parameter and software choices do or do not drive differences in phylogenetic inference.
By gathering the sequences, and making the unaligned files easily available to users, researchers can compare if applying any alternate alignment tool of their choice affects inferences.
Once sequences are aligned, they can apply and compare inferences from any Phylogenetic software.

@@

\section*{Conclusions}
Data repositories hold more information than meets the eye.
Beyond the main data, they are rich sources of metadata that can be leveraged
for the advantage of all areas of biology as well as the advancement of scientific
policy and applications.
Initial ideas about the data are constantly changed by results from new analyses.
Physcraper provides a framework for reproducible Phylogenetics that has the
potential to consistently provide context for these ideas, highlighting the
importance of data sharing and open science in the field, biology and science.

>>>>

Most of the default thresholds parameter values and software choices in the Physcraper pipeline are arbitrary.
We hope that by making the process of locating homologous sequences online reproducible,
and tracking what cutoffs are used, we make it easier for researchers to delve into the effect that different choices have on their inferences.
In addition, by providing the output files at each step of the analysis,
it is straightforward to assess how changing parameter and software choices do or do not drive differences in phylogenetic inference.
By gathering the sequences, and making the unaligned files easily available to users, researchers can compare if applying any alternate alignment tool of their choice affects inferences.
Once sequences are aligned, they can apply and compare inferences from any phylogenetic software.

@@

\section*{Conclusions}
Data repositories hold more information than meets the eye.
Beyond the main data, they are rich sources of metadata that can be leveraged
for the advantage of all areas of biology as well as the advancement of scientific
policy and applications.
Initial ideas about the data are constantly changed by results from new analyses.
Physcraper provides a framework for reproducible phylogenetics that has the
potential to consistently provide context for these ideas, highlighting the
importance of data sharing and open science in the field, biology and science.
